---
title: "To Beer or not to Beer"
author: "Perfect Presenter"
date: '2022-06-14'
output:
  ioslides_presentation: default
  beamer_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r map graphics}

library(BiocManager)
library(usmap)
library(stringr)
library(ggplot2)
library(readr)
library(dplyr)
library(tidyr)

setwd("/Volumes/Safe/Documents/Tutoring/R-Programing/BernardS")
Breweries <- read_csv("Breweries.csv")
Beers <- read_csv("Beers.csv", col_types = cols(Beer_ID = col_integer(), 
    Brewery_id = col_integer()), na = "NA")

# rename columns
rename(Beers, Brew_ID = Brewery_id,Beer=Name) -> Beers
rename(Breweries, state = State,Brewery=Name) -> Breweries

# group by state, count breweries in state, order by count and state.
Q1 <- Breweries %>% group_by(state) %>% summarise(Density = n()) %>% arrange(desc(Density),state)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output


```{r cars, echo=FALSE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Basics
1.	How many breweries are present in each state?
2.	Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.  (RMD only, this does not need to be included in the presentation or the deck.)

## Choropleth Map
### Density of breweries by state  
note: size of graphic controled  in Chunk header with the code for  
- fig.width  
- fig.height  
- fig.align
```{r fig.height = 4, fig.width = 4.5, fig.align = "right"}
plot_usmap(regions ="state", data = Q1, size=.2, values = "Density") + 
    scale_fill_continuous( low = "pink", high = "darkred", 
                         name = "Breweries", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(title = "Brewery Density by State") 
#+   theme(panel.background = element_rect(color = "grey90", fill = "lightblue")) 
```

note: does not consider state population. 

